EDA

### 2020-02-27 src/draft.Rmd
add mill rate/ assessed val v.s year plots

## R Markdown
```{r}
library(tidyverse)
library(dplyr)
library(here)
library(readxl)
```

@@

2019 tax is missing, we imputed 2019 tax using previous values
```{r}
tax_final <- read.csv("~/Desktop/tax_final.csv")
head(tax_final)

@@

2. pct_plots
plot pct change of mill rates
```{r}
dat_1<-data_final %>% subset(Municipalities == "Vancouver") %>% subset(TaxClassCode == "01")
dat_1
dat_1$rate_pct
plot(dat_1$rate_pct)

municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay")
tax.list<-c("01","05","06")
tax.list[1]
# overtall trend for tax class 1
for (i in 1:3){
  plot<-data_final %>% 
  filter(Municipalities %in% municipality.list) %>%
  filter(TaxClassCode == tax.list[i]) %>%
  ggplot(aes(x=Year, y=rate_pct, group=Municipalities, color=Municipalities)) +
    geom_line();
  print(plot)
}

>>>>

## R Markdown
```{r}
library(tidyverse)
library(dplyr)
library(here)
library(readxl)
```
```{r}
# all municipalities
municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay")
```

@@

2019 tax is missing, we imputed 2019 tax using previous values
```{r}
tax_final <- read.csv(here("data","tax_final.csv"))
head(tax_final)

@@

2. val_plots
```{r}
# mill rate vesus year for each municipality and tax class
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))
dat_rate <- assessment_aggregate %>% select(Year, AddressAssessorMunicipalityDesc, TaxClassCode, rate)
head(dat_rate)

dat_rate_1 <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="1") 
head(dat_rate_1)
rate_class1 <- dat_rate_1 %>% ggplot(aes(x=Year,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line()
rate_class1

dat_rate_5 <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="5") 
head(dat_rate_5)
rate_class5 <- dat_rate_5 %>% ggplot(aes(x=Year,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line()
rate_class5

dat_rate_6 <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="6") 
head(dat_rate_6)
rate_class6 <- dat_rate_6 %>% ggplot(aes(x=Year,y=rate,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line()
rate_class6

# plot assessed value vesus year for each municipality and tax class
dat_assess <- assessment_aggregate %>% select(Year, AddressAssessorMunicipalityDesc, TaxClassCode, assessTotal)
head(dat_assess)

dat_assess_1 <- dat_assess %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="1") 
head(dat_assess_1)
assess_class1 <- dat_assess_1 %>% ggplot(aes(x=Year,y=assessTotal,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line() + ggtitle("assessTotal for taxClass 1")
assess_class1

dat_assess_5 <- dat_assess %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="5") 
head(dat_assess_5)
assess_class5 <- dat_assess_5 %>% ggplot(aes(x=Year,y=assessTotal,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line() + ggtitle("assessTotal for taxClass 5")
assess_class5

dat_assess_6 <- dat_assess %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list) %>% filter(TaxClassCode=="6") 
head(dat_assess_6)
assess_class6 <- dat_assess_1 %>% ggplot(aes(x=Year,y=assessTotal,group=AddressAssessorMunicipalityDesc,color=AddressAssessorMunicipalityDesc)) + geom_line() + ggtitle("assessTotal for taxClass 6")
assess_class6
```

3. pct_plots
plot pct change of mill rates
```{r}
dat_1<-data_final %>% subset(Municipalities == "Vancouver") %>% subset(TaxClassCode == "01")
dat_1
dat_1$rate_pct
plot(dat_1$rate_pct)

tax.list<-c("01","05","06")
tax.list[1]
# overtall trend for tax class 1
for (i in 1:3){
  plot<-data_final %>% 
  filter(Municipalities %in% municipality.list) %>%
  filter(TaxClassCode == tax.list[i]) %>%
  ggplot(aes(x=Year, y=rate_pct, group=Municipalities, color=Municipalities)) +
    geom_line();
  print(plot)
}
